### 2018-03-27 Analysis/01-EffectCorrelationStats.Rmd
Automatic table build

```{r, eval = FALSE, echo = FALSE}
make.xtable(scenarios, caption = captions_pooled_scenarios, label = "Tab_pooledscenarios")
```

@@

```{r, eval = FALSE, echo = FALSE}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 2, label = "Tab_signif")
```

@@

```{r, eval = FALSE, echo = FALSE}
make.xtable(test_table, caption = cap_pool_scen_test, label = "Tab_pooledscenarios_test")
```

@@

```{r, eval = FALSE, echo = FALSE}
make.xtable(characters, caption = captions_pooled_characters, label = "Tab_pooledcharacters")
```

@@

```{r, eval = FALSE, echo = FALSE}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 3, label = "Tab_signif")
```

@@

```{r, eval = FALSE, echo = FALSE}
make.xtable(test_table, caption = cap_pool_char_test, label = "Tab_pooledscharacters_test")
```

@@

```{r, eval = FALSE, echo = FALSE}
make.xtable(taxa, caption = captions_pooled_taxa, label = "Tab_pooledtaxa")
```

@@

```{r, eval = FALSE, echo = FALSE}
make.xtable(test_table, caption = cap_pool_tax_test, label = "Tab_pooledstaxa_test")
```

@@

```{r, eval = FALSE, echo = FALSE}
make.xtable(methods, caption = captions_pooled_methods, label = "Tab_pooledmethod")
```

@@

```{r, eval = FALSE, echo = FALSE}
make.xtable(test_table, caption = cap_pool_met_test, label = "Tab_pooledsmethods_test")
```

@@

## Tables
make.xtable(sum_RF_best, caption = captions_summary[1], label = labels_summary[1])
make.xtable(sum_Tr_best, caption = captions_summary[2], label = labels_summary[2])
```

@@

## Tables
make.xtable(bc_RF_best, caption = captions_bc[1], label = labels_bc[1])
make.xtable(bc_Tr_best, caption = captions_bc[2], label = labels_bc[2])
```

@@

## Tables
make.xtable(wx_RF_best, caption = captions_wx[1], label = labels_wx[1])
make.xtable(wx_Tr_best, caption = captions_wx[2], label = labels_wx[2])
```

```{r, warning = FALSE}
## Pooling the data per scenarios
scenario_RF_norm <- multi.pool(whole_data, param = c("maxi", "mini", "rand"),
                               metric = "RF", best = "norm")
scenario_Tr_norm <- multi.pool(whole_data, param = c("maxi", "mini", "rand"),
                               metric = "Tr", best = "norm")
scenario_RF_null <- multi.pool(whole_data, param = c("maxi", "mini", "norm"),
                               metric = "RF", best = "rand")
scenario_Tr_null <- multi.pool(whole_data, param = c("maxi", "mini", "norm"),
                               metric = "Tr", best = "rand")

## Preparing the table labels
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)

## Combining the data into a table
scenarios <- pool.table(list(scenario_RF_norm, scenario_Tr_norm, scenario_RF_null, scenario_Tr_null),
                    comp.label = comp.labels, metric.label = metric.labels, label.param = "scenario")
```

```{r, echo = FALSE}
library(knitr)
## Setting the table captions
captions_pooled_scenarios <- paste("Summary statistics of the normalised distances to the best or null tree for the pooled scenarios.")

```{r, eval = FALSE, echo = FALSE}
library(xtable)
make.xtable(scenarios, caption = captions_pooled_scenarios, label = "Tab_pooledscenarios")
```

```{r}
## Applying an lm to all the data
results <- test.effect.aov(whole_data, formula = NTS ~ scenario, fun = lm)
```

```{r, eval = FALSE, echo = FALSE}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 2, label = "Tab_signif")
```

```{r, warning = FALSE}
## Summarise into a table
scenario_list <- list(scenario_RF_norm, scenario_Tr_norm, scenario_RF_null, scenario_Tr_null)
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)
test_table <- pair.test.table(scenario_list, comp.label = comp.labels, metric.label = metric.labels)
```

```{r, echo = FALSE}
## Caption
cap_pool_scen_test <- paste("Difference between the pooled scenarios. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)")

```{r, eval = FALSE, echo = FALSE}
make.xtable(test_table, caption = cap_pool_scen_test, label = "Tab_pooledscenarios_test")
```

```{r, warning = FALSE}
## Pooling the data per character
character_RF_norm <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "RF", best = "norm")
character_Tr_norm <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "Tr", best = "norm")
character_RF_null <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "RF", best = "rand")
character_Tr_null <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "Tr", best = "rand")

## Preparing the table labels
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)

## Combining the data into a table
characters <- pool.table(list(character_RF_norm, character_Tr_norm, character_RF_null, character_Tr_null),
                    comp.label = comp.labels, metric.label = metric.labels, label.param = "character")
```

```{r, eval = FALSE, echo = FALSE}
make.xtable(characters, caption = captions_pooled_characters, label = "Tab_pooledcharacters")
```

```{r}
## Applying an lm to all the data
results <- test.effect.aov(whole_data, formula = NTS ~ character, fun = lm)
```

```{r, eval = FALSE, echo = FALSE}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 2, label = "Tab_signif")
```

```{r, warning = FALSE}
## Summarise into a table
character_list <- list(character_RF_norm, character_Tr_norm, character_RF_null, character_Tr_null)
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)
test_table <- pair.test.table(character_list, comp.label = comp.labels, metric.label = metric.labels)
```

```{r, eval = FALSE, echo = FALSE}
make.xtable(test_table, caption = cap_pool_char_test, label = "Tab_pooledscharacters_test")
```

```{r, warning = FALSE}
## Pooling the data per taxa
taxa_RF_norm <- multi.pool(whole_data, param = c("t25", "t75", "t150"),
                               metric = "RF", best = "norm")
taxa_Tr_norm <- multi.pool(whole_data, param = c("t25", "t75", "t150"),
                               metric = "Tr", best = "norm")
taxa_RF_null <- multi.pool(whole_data, param = c("t25", "t75", "t150"),
                               metric = "RF", best = "rand")
taxa_Tr_null <- multi.pool(whole_data, param = c("t25", "t75", "t150"),
                               metric = "Tr", best = "rand")

## Preparing the table labels
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)

## Combining the data into a table
taxa <- pool.table(list(taxa_RF_norm, taxa_Tr_norm, taxa_RF_null, taxa_Tr_null),
                    comp.label = comp.labels, metric.label = metric.labels, label.param = "taxa")
```

```{r, eval = FALSE, echo = FALSE}
make.xtable(taxas, caption = captions_pooled_taxas, label = "Tab_pooledtaxa")
```

```{r}
## Applying an lm to all the data
results <- test.effect.aov(whole_data, formula = NTS ~ taxa, fun = lm)
```

```{r, eval = FALSE, echo = FALSE}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 2, label = "Tab_signif")
```

```{r, warning = FALSE}
## Summarise into a table
taxa_list <- list(taxa_RF_norm, taxa_Tr_norm, taxa_RF_null, taxa_Tr_null)
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)
test_table <- pair.test.table(taxa_list, comp.label = comp.labels, metric.label = metric.labels)
```

```{r, eval = FALSE, echo = FALSE}
make.xtable(test_table, caption = cap_pool_tax_test, label = "Tab_pooledstaxa_test")
```

```{r, warning = FALSE}
## Pooling the data per taxa
method_RF_norm <- multi.pool(whole_data, param = c("bayesian", "parsimony"),
                               metric = "RF", best = "norm")
method_Tr_norm <- multi.pool(whole_data, param =c("bayesian", "parsimony"),
                               metric = "Tr", best = "norm")
method_RF_null <- multi.pool(whole_data, param = c("bayesian", "parsimony"),
                               metric = "RF", best = "rand")
method_Tr_null <- multi.pool(whole_data, param = c("bayesian", "parsimony"),
                               metric = "Tr", best = "rand")

## Preparing the table labels
comp.labels <- c("Best", rep("", 3), "Null", rep("", 3))
metric.labels <- rep(c("RF", "", "Tr", ""), 2)

## Combining the data into a table
methods <- pool.table(list(method_RF_norm, method_Tr_norm, method_RF_null, method_Tr_null),
                    comp.label = comp.labels, metric.label = metric.labels, label.param = "method")
```

```{r, eval = FALSE, echo = FALSE}
make.xtable(methods, caption = captions_pooled_methods, label = "Tab_pooledmethod")
```

```{r}
## Applying an lm to all the data
results <- test.effect.aov(whole_data, formula = NTS ~ method, fun = lm)
```

```{r, eval = FALSE, echo = FALSE}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 2, label = "Tab_signif")
```

```{r, warning = FALSE}
## Summarise into a table
methods_list <- list(method_RF_norm, method_Tr_norm, method_RF_null, method_Tr_null)
comp.labels <- c("Best", rep("", 3), "Null", rep("", 3))
metric.labels <- rep(c("RF", "", "Tr", ""), 2)
test_table <- pair.test.table(methods_list, comp.label = comp.labels, metric.label = metric.labels)
```

```{r, eval = FALSE, echo = FALSE}
make.xtable(test_table, caption = cap_pool_met_test, label = "Tab_pooledsmethods_test")
```

# Individual results

```{r}
## Summarising the data
sum_RF_best <- apply.test(whole_data, "RF", "norm", NULL)
sum_Tr_best <- apply.test(whole_data, "Triples", "norm", NULL)
sum_RF_null <- apply.test(whole_data, "RF", "null", NULL)
sum_Tr_null <- apply.test(whole_data, "Triples", "null", NULL)
```

## Printing the tables
kable(sum_RF_best, row.names = FALSE, caption = captions_summary[1])
kable(sum_Tr_best, row.names = FALSE, caption = captions_summary[2])
kable(sum_RF_null, row.names = FALSE, caption = captions_summary[3])
kable(sum_Tr_null, row.names = FALSE, caption = captions_summary[4])
```

## Tables
make.xtable(sum_RF_best, caption = captions_summary[1], label = labels_summary[1])
make.xtable(sum_Tr_best, caption = captions_summary[2], label = labels_summary[2])
make.xtable(sum_RF_null, caption = captions_summary[3], label = labels_summary[3])
make.xtable(sum_Tr_null, caption = captions_summary[4], label = labels_summary[4])
```

```{r}
## Applying an lm to all the data with error
results <- test.effect.aov(whole_data,
  formula = NTS ~ scenario + (1|method) + (1|taxa) + (1|character), fun = lmer)
```

```{r, eval = FALSE, echo = FALSE}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 2, label = "Tab_signif")
```

```{r}
## Running the pairwise Bhattacharrya Coefficient analysis:
bc_RF_best <- apply.test(whole_data, "RF", "norm", bhatt.coeff)
bc_Tr_best <- apply.test(whole_data, "Triples", "norm", bhatt.coeff)
bc_RF_null <- apply.test(whole_data, "RF", "null", bhatt.coeff)
bc_Tr_null <- apply.test(whole_data, "Triples", "null", bhatt.coeff)

## Tables
kable(bc_RF_best, row.names = FALSE, digit = 3)
kable(bc_RF_best, row.names = FALSE, digit = 3)
kable(bc_RF_best, row.names = FALSE, digit = 3)
kable(bc_RF_best, row.names = FALSE, digit = 3)
```

```{r, echo = FALSE}
## Setting the table captions
captions_bc <- paste0("Bhattacharrya Coefficient (",rep(c("Robinson-Fould distance", "Triplets distance"), 2) ," from the ",c(rep("best", 2), rep("null", 2)), " tree)" , " between the different scenarios.")

## Printing the tables
kable(bc_RF_best, row.names = FALSE, caption = captions_bc[1], digit = 3)
kable(bc_Tr_best, row.names = FALSE, caption = captions_bc[2], digit = 3)
kable(bc_RF_null, row.names = FALSE, caption = captions_bc[3], digit = 3)
kable(bc_Tr_null, row.names = FALSE, caption = captions_bc[4], digit = 3)
```

```{r, echo = FALSE, eval = FALSE}
## Labels
labels_bc <- paste0("Tab_BC", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

## Tables
make.xtable(bc_RF_best, caption = captions_bc[1], label = labels_bc[1])
make.xtable(bc_Tr_best, caption = captions_bc[2], label = labels_bc[2])
make.xtable(bc_RF_null, caption = captions_bc[3], label = labels_bc[3])
make.xtable(bc_Tr_null, caption = captions_bc[4], label = labels_bc[4])
```

```{r, warning = FALSE}
## Running the pairwise Wilcox tests:
wx_RF_best <- apply.test(whole_data, "RF", "norm", wilcox.test)
wx_Tr_best <- apply.test(whole_data, "Triples", "norm", wilcox.test)
wx_RF_null <- apply.test(whole_data, "RF", "null", wilcox.test)
wx_Tr_null <- apply.test(whole_data, "Triples", "null", wilcox.test)

## Applying Bonferroni correction
for(column in c(5,7,9)) {
  wx_RF_best[,column] <- p.adjust(wx_RF_best[,column], method = "bonferroni")
  wx_Tr_best[,column] <- p.adjust(wx_Tr_best[,column], method = "bonferroni")
  wx_RF_null[,column] <- p.adjust(wx_RF_null[,column], method = "bonferroni")
  wx_Tr_null[,column] <- p.adjust(wx_Tr_null[,column], method = "bonferroni")
}
```

```{r, echo = FALSE}
## Setting the table captions
captions_wx <- paste0("Non-parametric Wilcoxon test (",rep(c("Robinson-Fould distance", "Triplets distance"), 2) ," from the ",c(rep("best", 2), rep("null", 2)), " tree)" , " between the different scenarios (p-values corrected using Bonferroni-Holm correction).")

## Printing the tables
kable(wx_RF_best, row.names = FALSE, caption = captions_wx[1], digit = 3)
kable(wx_Tr_best, row.names = FALSE, caption = captions_wx[2], digit = 3)
kable(wx_RF_null, row.names = FALSE, caption = captions_wx[3], digit = 3)
kable(wx_Tr_null, row.names = FALSE, caption = captions_wx[4], digit = 3)
```

```{r, echo = FALSE, eval = FALSE}
## Labels
labels_wx <- paste0("Tab_BC", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

## Tables
make.xtable(wx_RF_best, caption = captions_wx[1], label = labels_wx[1])
make.xtable(wx_Tr_best, caption = captions_wx[2], label = labels_wx[2])
make.xtable(wx_RF_null, caption = captions_wx[3], label = labels_wx[3])
make.xtable(wx_Tr_null, caption = captions_wx[4], label = labels_wx[4])
```

>>>>

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(scenarios, caption = captions_pooled_scenarios, label = "Tab_pooledscenarios", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 2, label = "Tab_signif")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(test_table, caption = cap_pool_scen_test, label = "Tab_pooledscenarios_test", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(characters, caption = captions_pooled_characters, label = "Tab_pooledcharacters", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 3, label = "Tab_signif")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(test_table, caption = cap_pool_char_test, label = "Tab_pooledscharacters_test", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(taxa, caption = captions_pooled_taxa, label = "Tab_pooledtaxa", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(test_table, caption = cap_pool_tax_test, label = "Tab_pooledstaxa_test", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(methods, caption = captions_pooled_methods, label = "Tab_pooledmethod", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(test_table, caption = cap_pool_met_test, label = "Tab_pooledsmethods_test", path = "../Writing/Tables/")
```

@@

## Tables
make.xtable(sum_RF_best, caption = captions_summary[1], label = labels_summary[1], path = "../Writing/Tables/")
make.xtable(sum_Tr_best, caption = captions_summary[2], label = labels_summary[2], path = "../Writing/Tables/")
```

@@

## Tables
make.xtable(bc_RF_best, caption = captions_bc[1], label = labels_bc[1], path = "../Writing/Tables/")
make.xtable(bc_Tr_best, caption = captions_bc[2], label = labels_bc[2], path = "../Writing/Tables/")
```

@@

## Tables
make.xtable(wx_RF_best, caption = captions_wx[1], label = labels_wx[1], path = "../Writing/Tables/")
make.xtable(wx_Tr_best, caption = captions_wx[2], label = labels_wx[2], path = "../Writing/Tables/")
```

### 2018-03-27 Analysis/02-EffectCorrelationFullResults.Rmd
Automatic table build

```{r, eval = FALSE, echo = FALSE}
library(xtable)
make.xtable(scenarios, caption = captions_pooled_scenarios, label = "Tab_pooledscenarios")
```

@@

```{r, eval = FALSE, echo = FALSE}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 2, label = "Tab_signif")
```

@@

```{r, eval = FALSE, echo = FALSE}
make.xtable(test_table, caption = cap_pool_scen_test, label = "Tab_pooledscenarios_test")
```

@@

```{r, eval = FALSE, echo = FALSE}
make.xtable(characters, caption = captions_pooled_characters, label = "Tab_pooledcharacters")
```

@@

```{r, eval = FALSE, echo = FALSE}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 2, label = "Tab_signif")
```

@@

```{r, eval = FALSE, echo = FALSE}
make.xtable(test_table, caption = cap_pool_char_test, label = "Tab_pooledscharacters_test")
```

@@

```{r, eval = FALSE, echo = FALSE}
make.xtable(taxas, caption = captions_pooled_taxas, label = "Tab_pooledtaxa")
```

@@

```{r, eval = FALSE, echo = FALSE}
make.xtable(test_table, caption = cap_pool_tax_test, label = "Tab_pooledstaxa_test")
```

@@

```{r, eval = FALSE, echo = FALSE}
make.xtable(methods, caption = captions_pooled_methods, label = "Tab_pooledmethod")
```

@@

```{r, eval = FALSE, echo = FALSE}
make.xtable(test_table, caption = cap_pool_met_test, label = "Tab_pooledsmethods_test")
```

@@

```{r, echo = FALSE, eval = FALSE}
## Labels
labels_summary <- paste0("Tab_Summary", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

## Tables
make.xtable(sum_RF_best, caption = captions_summary[1], label = labels_summary[1])
make.xtable(sum_Tr_best, caption = captions_summary[2], label = labels_summary[2])
make.xtable(sum_RF_null, caption = captions_summary[3], label = labels_summary[3])
make.xtable(sum_Tr_null, caption = captions_summary[4], label = labels_summary[4])
```

@@

```{r, echo = FALSE, eval = FALSE}
## Labels
labels_bc <- paste0("Tab_BC", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

## Tables
make.xtable(bc_RF_best, caption = captions_bc[1], label = labels_bc[1])
make.xtable(bc_Tr_best, caption = captions_bc[2], label = labels_bc[2])
make.xtable(bc_RF_null, caption = captions_bc[3], label = labels_bc[3])
make.xtable(bc_Tr_null, caption = captions_bc[4], label = labels_bc[4])
```

@@

```{r, echo = FALSE, eval = FALSE}
## Labels
labels_wx <- paste0("Tab_BC", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

## Tables
make.xtable(wx_RF_best, caption = captions_wx[1], label = labels_wx[1])
make.xtable(wx_Tr_best, caption = captions_wx[2], label = labels_wx[2])
make.xtable(wx_RF_null, caption = captions_wx[3], label = labels_wx[3])
make.xtable(wx_Tr_null, caption = captions_wx[4], label = labels_wx[4])
```

>>>>

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
library(xtable)
make.xtable(scenarios, caption = captions_pooled_scenarios, label = "Full_Tab_pooledscenarios", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 2, label = "Full_Tab_signif", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(test_table, caption = cap_pool_scen_test, label = "Full_Tab_pooledscenarios_test", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(characters, caption = captions_pooled_characters, label = "Full_Tab_pooledcharacters", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 2, label = "Full_Tab_signif")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(test_table, caption = cap_pool_char_test, label = "Full_Tab_pooledscharacters_test", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(taxa, caption = captions_pooled_taxa, label = "Full_Tab_pooledtaxa", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(test_table, caption = cap_pool_tax_test, label = "Full_Tab_pooledstaxa_test", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(methods, caption = captions_pooled_methods, label = "Full_Tab_pooledmethod", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(test_table, caption = cap_pool_met_test, label = "Full_Tab_pooledsmethods_test", path = "../Writing/Tables/")
```

@@

```{r, echo = FALSE, eval = FALSE}
## Labels
labels_summary <- paste0("Full_Tab_Summary", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

## Tables
make.xtable(sum_RF_best, caption = captions_summary[1], label = labels_summary[1], path = "../Writing/Tables/")
make.xtable(sum_Tr_best, caption = captions_summary[2], label = labels_summary[2], path = "../Writing/Tables/")
make.xtable(sum_RF_null, caption = captions_summary[3], label = labels_summary[3], path = "../Writing/Tables/")
make.xtable(sum_Tr_null, caption = captions_summary[4], label = labels_summary[4], path = "../Writing/Tables/")
```

@@

```{r, echo = FALSE, eval = FALSE}
## Labels
labels_bc <- paste0("Full_Tab_BC", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

## Tables
make.xtable(bc_RF_best, caption = captions_bc[1], label = labels_bc[1], path = "../Writing/Tables/")
make.xtable(bc_Tr_best, caption = captions_bc[2], label = labels_bc[2], path = "../Writing/Tables/")
make.xtable(bc_RF_null, caption = captions_bc[3], label = labels_bc[3], path = "../Writing/Tables/")
make.xtable(bc_Tr_null, caption = captions_bc[4], label = labels_bc[4], path = "../Writing/Tables/")
```

@@

```{r, echo = FALSE, eval = FALSE}
## Labels
labels_wx <- paste0("Full_Tab_BC", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

## Tables
make.xtable(wx_RF_best, caption = captions_wx[1], label = labels_wx[1], path = "../Writing/Tables/")
make.xtable(wx_Tr_best, caption = captions_wx[2], label = labels_wx[2], path = "../Writing/Tables/")
make.xtable(wx_RF_null, caption = captions_wx[3], label = labels_wx[3], path = "../Writing/Tables/")
make.xtable(wx_Tr_null, caption = captions_wx[4], label = labels_wx[4], path = "../Writing/Tables/")
```

### 2018-03-27 Writing/draft.tex
Automatic table build

%Packages
\usepackage{pdflscape}
\usepackage{fixltx2e}
\usepackage{textcomp}
\usepackage{fullpage}
\usepackage{float}
\usepackage{latexsym}
\usepackage{url}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{array}
\usepackage[version=3]{mhchem}
\usepackage{ifthen}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{amstext}
\usepackage{enumerate}
\usepackage[osf]{mathpazo}
\usepackage{dcolumn}
\usepackage{lineno}
\usepackage{dcolumn}
\usepackage{mathtools}
\usepackage{pdflscape}

@@

%MB: Why divide by 1/2 when you can just multiply by 2?
%TG: fair point. I've fixed it in the demonstration as well (supplementaries)

@@

\begin{table}[ht]
\centering
\begin{tabular}{ll|r|rr}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & maxi:mini & 0.588 & 439466.500 & \textbf{0.000} \\ 
   & maxi:rand & 0.894 & 347624.500 & \textbf{0.000} \\ 
   & mini:rand & 0.846 & 115008.500 & \textbf{0.000} \\ 
Tr & maxi:mini & 0.628 & 443049.500 & \textbf{0.000} \\ 
   & maxi:rand & 0.921 & 348074.000 & \textbf{0.000} \\ 
   & mini:rand & 0.825 & 113171.500 & \textbf{0.000} \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled scenarios. bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric Wilcoxon test (with Bonferonni-Holm correction), significant values are in bold.} 
\label{Tab_pooledscenarios_test}
\end{table}

@@

\begin{table}[ht]
\centering
\begin{tabular}{ll|r|rr}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & c100:c350 & \textbf{0.989} & 228495.000 & 0.174 \\ 
   & c100:c1000 & \textbf{0.983} & 218305.500 & \textbf{0.002} \\ 
   & c350:c1000 & \textbf{0.988} & 232832.500 & 0.643 \\ 
  Tr & c100:c350 & \textbf{0.965} & 203355.500 & \textbf{0.000} \\ 
   & c100:c1000 & \textbf{0.959} & 189064.000 & \textbf{0.000} \\ 
   & c350:c1000 & \textbf{0.983} & 226472.000 & 0.085 \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled number of characters. See Table \ref{Tab_pooledscenarios_test} for full caption.} 
\label{Tab_pooledscharacters_test}
\end{table}

@@

\begin{table}[ht]
\centering
\begin{tabular}{ll|r|rr}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & t25:t75 & \textbf{0.987} & 267274.500 & \textbf{0.003} \\ 
   & t25:t150 &\textbf{0.979} & 272359.500 & \textbf{0.000} \\ 
   & t75:t150 & \textbf{0.988} & 247619.500 & 1.000 \\ 
Tr & t25:t75 & \textbf{0.975} & 282017.500 & \textbf{0.000} \\ 
   & t25:t150 & \textbf{0.970} & 279730.000 & \textbf{0.000} \\ 
   & t75:t150 & \textbf{0.989} & 240414.500 & 1.000 \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled number of taxa. See Table \ref{Tab_pooledscenarios_test} for full caption.} 
\label{Tab_pooledstaxa_test}
\end{table}

@@

\begin{table}[ht]
\centering
\begin{tabular}{llrrr}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & bayesian:parsimony & 0.893 & 676940.500 & \textbf{0.000} \\ 
Tr & bayesian:parsimony & \textbf{0.982} & 547140.000 & 0.147 \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled methods. See Table \ref{Tab_pooledscenarios_test} for full caption.} 
\label{Tab_pooledsmethods_test}
\end{table}

>>>>

%Packages
\usepackage{fixltx2e}
\usepackage{textcomp}
\usepackage{fullpage}
\usepackage{float}
\usepackage{latexsym}
\usepackage{url}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{array}
\usepackage[version=3]{mhchem}
\usepackage{ifthen}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{amstext}
\usepackage{enumerate}
\usepackage[osf]{mathpazo}
\usepackage{dcolumn}
\usepackage{lineno}
\usepackage{pdflscape}

@@

@@

\input{Tables/Tab_pooledscenarios_test.tex}

% \begin{table}[ht]
% \centering
% \begin{tabular}{ll|r|rr}
%   \hline
% metric & test & bhatt.coeff & statistic & p.value \\ 
%   \hline
% RF & maxi:mini & 0.588 & 439466.500 & \textbf{0.000} \\ 
%    & maxi:rand & 0.894 & 347624.500 & \textbf{0.000} \\ 
%    & mini:rand & 0.846 & 115008.500 & \textbf{0.000} \\ 
% Tr & maxi:mini & 0.628 & 443049.500 & \textbf{0.000} \\ 
%    & maxi:rand & 0.921 & 348074.000 & \textbf{0.000} \\ 
%    & mini:rand & 0.825 & 113171.500 & \textbf{0.000} \\ 
%    \hline
% \end{tabular}
% \caption{Difference between the pooled scenarios. bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric Wilcoxon test (with Bonferonni-Holm correction), significant values are in bold.} 
% \label{Tab_pooledscenarios_test}
% \end{table}

@@

\input{Tables/Tab_pooledscharacters_test.tex}

@@

\input{Tables/Tab_pooledstaxa_test.tex}

@@

\input{Tables/Tab_pooledsmethods_test.tex}
